---
title: "TD2 - Movement Ecology models"
author: "Marie-Pierre Etienne"
date: "October, 2023"
output: 
  xaringan::moon_reader:
    css: [  'metropolis', 'hygge', 'mpe_pres.css']
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
require(ggplot2)
```


# Four classical movement models
We denote by $X_k$ the position at time $t_k$ et $V_k$ the velocity.

## Random walk on $\mathbb{R}^2$

$$X_{k+1} = X_k + \varepsilon_{k+1}, \quad (\varepsilon_{k}) Normal i.i.d random noise$$
  
## Auto regressive Model on $\mathbb{R}^2$ - Central place behaviour

$$X_{k+1} =\mu +  \rho (X_k - \mu)  + \varepsilon_{k+1}, \quad (\varepsilon_{k}) Normal i.i.d random noise$$
  
## Integrated Random walk 
  
$$V_{k+1} = V_k + \varepsilon_{k+1}, X_{k+1} = X_k +  V_{k+1} + \nu_{k+1}\quad (\varepsilon_{k}) Normal i.i.d random noise$$
  
## Integrated Correlated Random walk 
  
$$V_{k+1} = \mu + \rho(V_k-\mu) + \varepsilon_{k+1}, X_{k+1} = X_k +  V_{k+1} + \nu_{k+1}\quad (\varepsilon_{k}) Normal i.i.d random noise$$
  
  
# Four classical movement models - simulation

Write 4 functions to simulate this movement model, and compare for the same level of noise, starting from $(0,0)$ the first time the distance to $(0,0)$ exceeds $25$,

Change the value of $\mu$ to measure its impact.

# How to integrate the landscape ?

* A natural barrier

* A jaguar in a cage, how to deal with the limits of the cage ? What does it change for the stationnary distribution ?

.pull-left[

* a spatiallly structure covariate]

.pull-right[

```{r}
library(geoR)
library(tidyverse)
pred.grid <-  expand.grid(x=seq(-20,20, l=51), y=seq(-20,20, l=51))
sim <- grf(grid = pred.grid,  cov.pars=c(10, 8))  ##param variand and portee
cov_data <- sim[[1]] %>% 
  as_tibble() %>% 
  mutate(cov1 = sim[[2]])  
image(sim)
```
]
